The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
add 750m

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology. We
aggregated the 30 m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation
occurred using a modal moving window method using a circular window
corresponding to the above scales [@Graham_2019a]. We assume 30 m and 100 m
represents fine-scale decision making for caribou during foraging, while
re-sampling at 500 m and 1000 m represents the scale at which caribou tend to
select and avoid habitat (Bastille-Rousseau et al. 2017).

>>>>

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology. We
aggregated the 30 m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, 750 m and 1000 m. Aggregation
occurred using a modal moving window method using a circular window
corresponding to the above scales [@Graham_2019a]. We assume 30 m and 100 m
represents fine-scale decision making for caribou during foraging, while
re-sampling at 500 m , 750 m and 1000 m represents the scale at which caribou tend to
select and avoid habitat (Bastille-Rousseau et al. 2017).
